### 2011-09-14 docs/FAQ/faq.tex
add note about BOXLIB_HOME directory

>>>>

\item {\em The code doesn't compile, but complains right away that there
   is ``{\tt No rule to make target `fabio\_c.c', needed by `t/Linux.gfortran.mpi/c.depends'}''}

   The environment variable {\tt BOXLIB\_HOME} needs to be the full path
   to the {\tt BoxLib} directory.  You cannot use `{\tt $\sim$}' as a shortcut
   for your home directory.
